---
title: "Untitled"
author: "Md Jalal Uddin"
date: "October 30, 2016"
output: html_document
---
Problem Set 1. Playing with PageRank.

Let's use the 6 page universe that we had in the course notes.Form the A matrix. Then, introduce decay and form the B matrix as we did in the course notes.

```{r}
(A <- matrix(c(0, 1/2, 1/2, 0, 0,  0,
              0, 0, 0, 1, 0, 0,
              1/3, 1/3, 0, 0, 1/3, 0,
              0, 0, 0, 0, 1/2, 1/2,
              0, 0, 0, 1/2, 0, 1/2,
              0, 0, 0, 1, 0, 0), nrow=6))

(A <- matrix(c(0, 1/2, 1/2, 0, 0,  0,
              0, 0, 1, 0, 0, 0,
              1/4, 1/4, 0, 0, 1/4, 1/4,
              0, 0, 0, 0, 1/2, 1/2,
              0, 0, 0, 1/2, 0, 1/2,
              0, 0, 1/2, 1/2, 0, 0), nrow=6))


```


```{r}
decay <- 0.85

(B <- decay*A + ((1- decay)/6))

```

Start with a uniform rank vector r and perform power iterations on B till convergence.
That is, compute the solution r = Bn × r. Attempt this for a sufficiently
large n so that r actually converges.

```{r}
(r <- matrix(c(1/6,1/6,1/6,1/6,1/6,1/6),nrow=6))

```

Define PageRank function

```{r}
func_iteration <- function (B,r,p) {

X <- B%*%r
t <- diag(6)

  for (i in 1:p) {
       X<- t%*%X
       X<- B%*%X
       i<-i+1
      }
return(X)
}

#finding PageRank function with 10 iteration. 
func_iteration(B,r,10)

#finding PageRank function with 20 iteration. 
func_iteration(B,r,20)

#finding PageRank function with 20 iteration. 
func_iteration(B,r,30)

```

Compute the eigen-decomposition of B and verify that you indeed get an eigenvalue
of 1 as the largest eigenvalue and that its corresponding eigenvector is the same
vector that you obtained in the previous power iteration method. Further, this
eigenvector has all positive entries and it sums to 1.

```{r}
# Eigen values
(Eigen_v <- eigen(B, only.values = FALSE)$vectors[,1]) 

# Eigen vector
eigen_vectors<- Eigen_v * (1/ sum(Eigen_v ))
data.frame(eigen_vectors)

```

Use the graph package in R and its page.rank method to compute the Page Rank
of the graph as given in A. Note that you don't need to apply decay. The package
starts with a connected graph and applies decay internally. Verify that you do get
the same PageRank vector as the two approaches above.

```{r}
library(igraph)

graph_URl <- graph.adjacency(t(A), weighted = T, mode = "directed")
plot(graph_URl)

Page_Rank1 <- round((page.rank(graph_URl)$vector), 7)

print(Page_Rank1)

```


```{r}
# quick validation of equality of the above two approaches.

isTRUE(round(func_iteration(B,r,20), 4) == round(eigen_vectors, 4) && round(func_iteration(B,r,20), 4) == round(Page_Rank1, 4))

```


